---
Bhoruka analysis
---
Try to find out if there is any relationship between the power, wind direction

##Reading teh data
```{r}
turbineData<- read.csv(file="files/consolidated.csv", header=TRUE, sep=",")
str(turbineData)

curveIndexes1<-seq(from=1,to=9,by=1)
curveIndexes2<-seq(from=10,to=29,by=1)

p1=paste0("WTG00",curveIndexes1)
p2=paste0("WTG0",curveIndexes2)
curveIndexes=c(p1,p2)
curveIndexes1=as.factor(curveIndexes)
```


##Get compass Direction: Based on the direction of the wind in degrees , it returns the compass direction
```{r}
getCompassDirection=function(heading){
  if(heading>348.75 & heading <359.99)
    "N"
  else if(heading>=0 & heading <11.25)
    "N"
  else if(heading>11.25 & heading <33.75)
    "NNE"
  else if(heading>33.75 & heading <56.25)
    "NE"
  else if(heading>56.25 & heading <78.75)
    "ENE"
  else if(heading>78.75 & heading <101.25)
    "E"
  else if(heading>101.25 & heading <123.75)
    "ESE"
  else if(heading>123.75 & heading <146.25)
    "SE"
  else if(heading>146.25 & heading <168.75)
    "SSE"
  else if(heading>168.75 & heading <191.25)
    "S"
  else if(heading>191.25 & heading <213.75)
    "SSW"
  else if(heading>213.75 & heading <236.25)
    "SW"
  else if(heading>236.25 & heading <258.75)
    "WSW"
  else if(heading>258.75 & heading <281.25)
    "W"
  else if(heading>281.25 & heading <303.75)
    "WNW"
  else if(heading>303.75 & heading <326.25)
    "NW"
  else if(heading>326.25 & heading <348.75)
    "NNW"
}



```


##Create teh necessary data frames represting power, nacelleDirecation, wind speed and compass direction. This is a derived data

```{r}
tfpower=subset(turbineData,turbineData$Parameter=='Power'&turbineData$SystemName==curveIndexes[1])[4]
tfWindSpeed=subset(turbineData,turbineData$Parameter=='Wind speed'&turbineData$SystemName==curveIndexes[1])[4]
tfNacelle=  subset(turbineData,turbineData$Parameter=='Nacelle position'&turbineData$SystemName==curveIndexes[1])[4]
#add the compass directiuons for the Nacelle
tfCompassDirection=subset(turbineData,turbineData$Parameter=='Nacelle position'&turbineData$SystemName==curveIndexes[1])[4]

for(i in 1:29){
  tfpower[,curveIndexes[i]]=subset(turbineData,turbineData$Parameter=='Power'&turbineData$SystemName==curveIndexes1[i])[3]
  tfWindSpeed[,curveIndexes[i]]=subset(turbineData,turbineData$Parameter=='Wind speed'&turbineData$SystemName==curveIndexes1[i])[3]
  tfNacelle[,curveIndexes[i]]=subset(turbineData,turbineData$Parameter=='Nacelle position'&turbineData$SystemName==curveIndexes1[i])[3]
  
}

#add the compass direction
for(i in 1:29){
  
  tfCompassDirection[,curveIndexes[i]]=sapply(tfNacelle[,curveIndexes[i]],getCompassDirection)

}

```

##data cleaning
* 1. First removing the localtime column
* 2. Not all the data is interesting. The -ve power observations are of not much value and they will actually lower the average power per turbine. So removing the observations 1-11 and 33-39


```{r}
tfpower=tfpower[,c(2:30)]
tfpower=tfpower[12:32,]

tfNacelle=tfNacelle[,c(2:30)]
tfNacelle=tfNacelle[12:32,]

tfWindSpeed=tfWindSpeed[,c(2:30)]
tfWindSpeed=tfWindSpeed[12:32,]

tfCompassDirection=tfCompassDirection[,c(2:30)]
tfCompassDirection=tfCompassDirection[12:32,]

curveNames=names(tfpower)

```

##Summary Statistics
Some of the userful stats from the data are max,min power, avg power, avg wind direction, max-min wind direction

```{r}

turbineSummaryMat=matrix(1:29*4,nrow=29,ncol=4)
rownames(turbineSummaryMat) <- curveNames[1:29]
colnames(turbineSummaryMat)<-c("maxWindSpeed","minWindSpeed","maxNacAngle","minNacAngle")
turbineSummary=as.data.frame(turbineSummaryMat)
turbineSummary$maxWindSpeed=sapply(tfWindSpeed,max)
turbineSummary$minWindSpeed=sapply(tfWindSpeed,min)
turbineSummary$maxNacAngle=sapply(tfNacelle,max)
turbineSummary$minNacAngle=sapply(tfNacelle,min)
turbineSummary$spreadNacAngle=turbineSummary$maxNacAngle-turbineSummary$minNacAngle


windDirections=rep(0,29)
for ( i in 1:29)
{
  windDirections[i]=names(sort(table(sapply(tfNacelle[,i],getCompassDirection)),decreasing = TRUE)[1])
}

turbineSummary$windDirection=as.factor(windDirections)
turbineSummary$maxPower=sapply(tfpower,max)
turbineSummary$minPower=sapply(tfpower,min)
turbineSummary$avgPower=sapply(tfpower,mean)
turbineSummary$totalPower=sapply(tfpower,sum)

str(turbineSummary)


```
##distribution of power wrt wind directioon

```{r}
sort(by(turbineSummary$totalPower,turbineSummary$windDirection,sum),decreasing = TRUE)


```

##Plots of wind directaions

```{r}
#plottig the winddirections and the windspeed
library(plotrix)
for (i in 1:29){
  
  spread=max(tfNacelle[,i])-min(tfNacelle[,i])
  label=paste(curveNames[i],spread)
  polar.plot(tfWindSpeed[,i],polar.pos=tfNacelle[,i],start=90,clockwise=TRUE,rp.type="p",
             point.symbols=19,boxed.radial=FALSE, 
             radial.labels="",main = label,lwd=2,line.col=4)

  
}

```


##correlation analysis for the power data

```{r}

correlationMatrix<-cor(tfpower,use='pairwise.complete.obs')
correlationMatrix[correlationMatrix<0.95]<-NA
filteredList<-apply(correlationMatrix,1,sort,decreasing=TRUE)

#correlationNascMatrix<-cor(tfNacelle,use='pairwise.complete.obs')
#correlationNascMatrix[correlationNascMatrix<0.95]<-NA
#filteredListNasc<-apply(correlationNascMatrix,1,sort,decreasing=TRUE)

```

##draw curves

```{r}

drawCurves=function(curve1,curve2)
{

plot(tfpower[,curve1],type='l',ylab = curve1,xlab = curve2)
points(tfpower[,curve2],col="green",type='l')

#points(tfWindSpeed[,curve1],col="yellow",type='l')
#points(tfWindSpeed[,curve2],type='l')
#points(tfNacelle[,curve1],col="red",type='l')
#points(tfNacelle[,curve2],col="blue",type='l')
}



```

draw the curves for a particular turbine with respect to the other turbines to see 
how it is performing 

```{r}

for (i in 1:29){
  drawCurves(curveNames[3],curveNames[i])
}

```

##
1.Some of the unkowns
2. what is the operating state parameter..these are some of the states that determine if the turbine is working properly or not
3.what is availability parameter
4. what is State and Fault
5. Can we find out the turbines which are performing high than the one that are not performing that much
6. Can we correlate the power output with the wind directions





