Read the data from the database

```{r}
library(RMySQL)
mydb = dbConnect(MySQL(), user='root', password='', dbname='pgs', host='localhost')

turbineData <- dbGetQuery(mydb, "Select * from turbineData order by timestamp")
str(turbineData)


curveIndexes1<-seq(from=1,to=9,by=1)
#curveIndexes2<-c(10:20,22,23,25:28,31,34,38,40:43,45:52,55,56)
curveIndexes2<-seq(from=10,to=56,by=1)
curveIndexesCombined=c(paste0("WTG00",1:9),paste0("WTG0",10:20),"WTG022","WTG023",
                       paste0("WTG0",25:28),"WTG031","WTG034","WTG038",paste0("WTG0",40:43),
                       paste0("WTG0",45:48),"WTG050","WTG051","WTG052","WTG055","WTG056")

p1=paste0("WTG00",curveIndexes1)
p2=paste0("WTG0",curveIndexes2)
curveIndexes=c(p1,p2)
curveIndexes1=as.factor(curveIndexes)
curveIndexes1=curveIndexes

numberOfTurbines=length(curveIndexesCombined)
curveNames=curveIndexesCombined
```
Define the function to get the compass directions

```{r}
getCompassDirection=function(heading){
  if (is.na(heading))
    NA
  if(heading>348.75 & heading <360.1)
    "N"
  else if(heading>=0 & heading <11.25)
    "N"
  else if(heading>11.25 & heading <33.75)
    "NNE"
  else if(heading>33.75 & heading <56.25)
    "NE"
  else if(heading>56.25 & heading <78.75)
    "ENE"
  else if(heading>78.75 & heading <101.25)
    "E"
  else if(heading>101.25 & heading <123.75)
    "ESE"
  else if(heading>123.75 & heading <146.25)
    "SE"
  else if(heading>146.25 & heading <168.75)
    "SSE"
  else if(heading>168.75 & heading <191.25)
    "S"
  else if(heading>191.25 & heading <213.75)
    "SSW"
  else if(heading>213.75 & heading <236.25)
    "SW"
  else if(heading>236.25 & heading <258.75)
    "WSW"
  else if(heading>258.75 & heading <281.25)
    "W"
  else if(heading>281.25 & heading <303.75)
    "WNW"
  else if(heading>303.75 & heading <326.25)
    "NW"
  else if(heading>326.25 & heading <348.75)
    "NNW"
  
}

meanDirection=function(x)
{
  #names(sort(table(x),decreasing = TRUE))[1]
  sort(table(x),decreasing = TRUE)

}

changingDirection=function(x)
{
  ll=length(names(sort(table(x))))
  ss=sum(table(x))
  as.character(c(ll,":",ss))
}

countUniqueDirections=function(x)
{
  ll=length(names(sort(table(x))))
  return(ll);
}

countNumberOfReadings=function(x)
{
  ss=sum(table(x))
  return(ss)
}

myMean=function(x)
{
  ss=sum(table(x))
  #return(ll);
  return(sum(x)/ss)
}


findMeanDirection=function(x,monthName)
{
  #i think the mean diraction can be found by first c
  #first get the nascelle disrtibuted by months
  nacelleMon=subset(x$nacelle,x$month==monthName)
  directions=sapply(nacelleMon,getCompassDirection)
  directions=unlist(directions)
  sort(table(directions),decreasing = TRUE)
  
}





```


```{r}
df=turbineData
df$compassDirection=lapply(df$nacelle,getCompassDirection)
#df$compassDirection=unlist(df$compassDirection)
tt<-as.Date(df$timestamp)
df$days=as.factor(format(tt,'%d_%b'))
df$month=as.factor(format(tt,'%b'))

newOrder=unique(format(tt,'%d'))
#months=unique(df$month)
months=c("Sep","Aug","Jul","Jun")
colors=c("red","green","blue","yellow")
library(plotrix)
#newfactors1=paste0(newOrder[1:30],"_",months[1])
#newfactors2=paste0(newOrder[1:31],"_",months[2])
#newfactors=c(newfactors1,newfactors2)


#df$days = factor(df$days,levels(x)[c(4,5,1:3)])

#draw power plots of this turbine
for(i in c(1:numberOfTurbines)){
 i=2    
 #individualTurbineData=df
 individualTurbineData=subset(df,df$turbineId==curveIndexesCombined[i])
 unsortedPowerByDay=by(individualTurbineData$power,individualTurbineData$days,sum)
 #sortedPowerByDayJul=unsortedPowerByDay[seq(1,61,2)]
 #sortedPowerByDayJun=unsortedPowerByDay[seq(2,61,2)]
 #sortedPowerByDay=c(sortedPowerByDayJul,sortedPowerByDayJun)
 #library(ggplot2)
 barplot(unsortedPowerByDay,main = paste0("power curve for ",curveNames[i]),col=colors,legend=months,beside=TRUE)
 #qplot(factor(months), data=unsortedPowerByDay, geom="bar", fill=factor(months))
 #ggplot(unsortedPowerByDay, aes(factor(months)))
 
 
 
 unsortedTemperatureByDay=by(individualTurbineData$temperature,individualTurbineData$days,mean)
 barplot(unsortedTemperatureByDay,main = paste0("temp curve for",curveNames[i]),col=colors,legend=months,beside=TRUE)
 
 
 unsortedAvgPowerByDay=by(individualTurbineData$power,individualTurbineData$days,mean)
 barplot(unsortedAvgPowerByDay,main = paste0("Avg power curve for ",curveNames[i]),col=colors)
 
 
 #individualTurbineData$compassDirection=as.factor(individualTurbineData$compassDirection)
 #similarly for the wind speed
 unsortedAverageWindSpeedByDay=by(individualTurbineData$windspeed,individualTurbineData$days,myMean)
 barplot(unsortedAverageWindSpeedByDay,main = paste0("wind curve for ",curveNames[i]),col=colors)
 
 
 #monthly
 monthlyPowerProduced=tapply(individualTurbineData$power,individualTurbineData$month,sum)
 monthlyAvgWindSpeed=tapply(individualTurbineData$windspeed,individualTurbineData$month,myMean)
 #monthlyAvgNascellePosition=tapply(individualTurbineData$nacelle, individualTurbineData$month,mean)
 #monthlyCompassDirection=sapply(monthlyAvgNascellePosition,getCompassDirection)
 monthlyAvgTemperature=tapply(individualTurbineData$temperature,individualTurbineData$month,mean)
 monthMat=data.frame(matrix(ncol=3,nrow=length(months)))
 monthMat[,1]=monthlyPowerProduced
 monthMat[,2]=monthlyAvgWindSpeed
 monthMat[,3]=monthlyAvgTemperature
 #monthMat[,4]=monthlyCompassDirection
 rownames(monthMat)=names(monthlyPowerProduced)
 colnames(monthMat)=c("Total Power","Avg Wind Speed","Avg Temp")
 print(monthMat)
 
 
 
 
 
 #direction distributions
# windDirectionperDay=by(individualTurbineData$compassDirection,individualTurbineData$day#s,meanDirection)
  
 
 #plot(individualTurbineData$days,individualTurbineData$power,main=curveIndexesCombined[i])
 
 #plot(individualTurbineData$days,individualTurbineData$power,main=curveIndexesCombined[i],type='l')
 
 

  
  
  for(j in c(1:length(months))){
  #subsetDataForJune=subset(individualTurbineData,individualTurbineData$month=="Jun")
  #subsetDataForJuly=subset(individualTurbineData,individualTurbineData$month=="Jul")
  directions=findMeanDirection(individualTurbineData,months[j])
  cat("Directions for the month",months[j])
  print(directions)
  
  subsetData=subset(individualTurbineData,individualTurbineData$month==months[j])  
  spread=max(subsetData$nacelle)-min(subsetData$nacelle)
  label=paste(curveNames[i],"for month",months[j],spread)
  polar.plot(subsetData$windspeed,polar.pos=subsetData$nacelle,
             start=90,clockwise=TRUE,rp.type="s",
             point.symbols=19,boxed.radial=FALSE, 
             radial.labels="",main = label,lwd=2,line.col=4) 

  #polar.plot(subsetDataForJuly$windspeed,polar.pos=subsetDataForJuly$nacelle,
   #          start=90,clockwise=TRUE,rp.type="s",
    #         point.symbols=19,boxed.radial=FALSE, 
     #        radial.labels="",main = label,lwd=2,line.col=3) 

  }
}



```

Importnat thing to note is that in this case the nacelled is restricted to only one section


```{r}

individualTurbineData=subset(df,df$turbineId==curveIndexesCombined[1])
train=individualTurbineData[1:1500,]
test=individualTurbineData[1501:2559,]
#need to relevel the factor variables
model1=lm(power~windspeed+nacelle,data=individualTurbineData)
summary(model1)

#cart model




```


Few observations
1. the month of july is the maximum. even though we have some missing data but it is still maximum
2. the month of Jun is second best
3. In aug the wind has started to decrease
4. Sept is a lean month with less power produced

The nacelle movement is restricted to few directions is case of june and august while in june and september there has been activity in the movement of nacelle
When do we move nacelled?


